---
title: "Intro to R HW"
author: "George Tryfiates"
date: "8 October 2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE, comment=NA, message = FALSE, warning = FALSE, options(scipen = 999, digits = 4))
#multicollinearity
library(GGally)
library(mctest)
library(corpcor)
library(ggfortify)
library(ggrepel)
library(AER)
library(tidyverse)
#library(summariser)
#don't rly need summariser
library(summarytools)
library(estimatr)
library(readxl)
library(plm) 
#panel data
library(stargazer) 
#we prolly only need jtoools
library(magrittr) 
#pipe data^. mutating data (create interaction variable)
library(janitor)
#broom- allows you to change the case of all the variables
library(moderndive)
#little more versatile internally, but not very pretty
library(jtools)
#"journal tools" regression output pretty
library(huxtable)
library(readxl)
library(flextable)
library(RColorBrewer)

```

Set the Working Directory:

```{r}
setwd("C:/Users/seeuo/Documents/Tech Talent South/TTS_Data_Science/module13")
```


Read in the Data (I put it in excel):

```{r}
meta <- read_xlsx("meta.xlsx")
meta
```

Select only sex and treatment: 

```{r}
meta %>% select(sex, treatment)
```

Saved the dataframe as a tibble to make things easier

```{r}
meta %<>% as_tibble()
```

Renamed the index to index:

```{r}
meta %<>% rename(index = ...1)
```

Selecting certain rows:

```{r}
filt <- c(5, 7, 9, 10)
meta %>% slice(filt)
```

Filtering rows:

```{r}
meta %>% filter(treatment == "P")
```

Filtering rows of selected columns:

```{r}
meta %>% filter(myc > 5000) %>% select(stage, treatment)
```

Selecting all but treatment:

```{r}
meta %>% select(-treatment)
```

Selecting all but certain rows (this is long and clunky :P ):

```{r}
filt = c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE)

meta[filt, ]
```

Slicing rows:

```{r}
meta[1:6, ]
```

Adding a column:

```{r}
pre_treatment = c(T, F, F, F, T, T, F, T, F, F, T, T)
meta %<>% mutate(pre_treatment)
```

```{r}
meta
```

Renaming the columns as letters:

```{r}
meta %<>% rename(A = index, B =sex,C = stage, D = treatment , E = myc, F = pre_treatment)
```

```{r}
meta
```


